---
title: "Cleaning SRET"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=14, fig.height=12)
```

# Load packages, source functions, set plot parameters  

```{r, results = hide}
# Load packages, source functions, set plot parameters, get behavioral and DIC dfs   
packages_to_load <- c(
  "dplyr",
  "tidyverse",
  "latex2exp",
  "purrr",
  "tidyr",
  "rlang",
  "patchwork",
  "haven",
  "RWiener",
  "ggplot2",
  "psych"
)
sapply(packages_to_load, require, character.only=TRUE)

sf <- function() sapply(fs, source)
fs <- c(
  paste0('./Modules/', list.files('./Modules/'))  
)
sf()
SetPlotPars()
```

# Load Data  

```{r}
# Get main SRET_CTL df..
bx_df <- read.csv("./../../data/raw_files/sret_from_KW_06_08_20.csv")
# .. and df with some extra info to put in 

extra_df_full <- 
  read.csv("./../../data/raw_files/tx_cond+ffmq+maas_from_KW_6.24.2020.csv")
```


Do some cleanup  
```{r}
# 12.10 adding but not exporting item 
bx_dfs <- # Short df
  setNames(bx_df[c("ID", "Time", "RT",  
                   "VALENCE", "CONDITION", "RESPONSE", "CORRECTNESS", "CAPS", "ITEM")], 
         c("subj_idx", "session",  "rt", 
                    "valence", "task", "response", "correct", "ctl_type", "item"))
```


Some original code is left commented in the below from what was used to create `s_bdf` for model running originally,
following an R upgrade that apparently led to stricter factor change rules (eg. relevel on character vec doesn't auto-convert to factor first)  

```{r}
# Numeric codes 
#bx_dfs$task_n <- as.numeric(bx_dfs$task)-1 # 1 is SRET, 0 is CTL  # No longer needed 
#bx_dfs$session <- relevel(bx_dfs$session, "Pre")
bx_dfs$session <- relevel(factor(bx_dfs$session), "Pre")
# Drop miss trials from dataset
bx_dfs <- bx_dfs[!bx_dfs$response=="MISS", ]
```

```{r}
bx_dfs$response <- as.numeric(droplevels(factor(bx_dfs$response)))-2
bx_dfs <- bx_dfs[!bx_dfs$response==-1, ] # Drop one missed trial that was labeled -1

# Recode correct 
bx_dfs$correct_c <- as.character(bx_dfs$correct)
bx_dfs[bx_dfs$task == "case" & bx_dfs$correct_c=="correct", "correct"] <- 1
bx_dfs[bx_dfs$task == "case" & bx_dfs$correct_c=="incorrect", "correct"] <- 0
# (^changed after R updated 2022 because stricter scheme disallows below)
#bx_dfs$correct <- relevel(factor(bx_dfs$correct), "incorrect")
#bx_dfs$correct <- relevel(bx_dfs$correct, "incorrect")
#bx_dfs$correct_n <- as.numeric(bx_dfs$correct)-1

# Note negative is the reference level so increases in posterior indicate salutary changes 
#bx_dfs$valence_n <- as.numeric(bx_dfs$valence)-1
bx_dfs$valence_n <- as.numeric(relevel(factor(bx_dfs$valence), "negative"))-1

# Pre is reference level
bx_dfs$session_n <- as.numeric(bx_dfs$session)-1

# Spot checks 
# table(bx_dfs$response)
# table(bx_dfs[bx_dfs$task=="case", "response"])
#which(is.na(bx_dfs$response))
#table(as.numeric(bx_dfs$correct)-1)
#bx_dfs %>% select(valence, valence_n)
```

```{r}
#table(bx_dfs$subj_idx, bx_dfs$session)
bx_dfs <- bx_dfs %>% filter(rt > 200)
bx_dfs$rt <- bx_dfs$rt/1e3 
# Add task switch var 
#bx_dfs$task_switch <- rep(NA, nrow(bx_dfs))
bx_dfs <- lapply(split(bx_dfs, bx_dfs$subj_idx), function (x) {
  x$task_switch <- 
    c(0, if_else((x[2:nrow(x), "task"]==x[1:nrow(x)-1, "task"]), 0, 1))
x  
}) %>% bind_rows()
# bx_dfs %>% filter(subj_idx==3) # Spot checks
# bx_dfs %>% filter(subj_idx==105)
table(bx_dfs$task_switch) # About even number
```

```{r}
c_bdf <- bx_dfs %>% filter(task=="case")
c_bdf$correct_n <- as.numeric(c_bdf$correct)

# Only one pt with fewer than 70% correct  
correct_sum <- 
  c_bdf %>%  group_by(session, subj_idx) %>% 
    summarize(m=mean(correct_n))

which(correct_sum$m < .7)

low_perf_pt <- correct_sum[which(correct_sum$m < .7), "subj_idx"] # Pt performing ~ chance at post  

# Drop this pt's data  
bx_dfs <- bx_dfs %>% filter(!subj_idx == 36)

# Drop the accidentally enrolled pt (see KW email exchange)  
bx_dfs <- bx_dfs %>% filter(!subj_idx==139)
```

Center for more interpretable coefs  
```{r}
bx_dfs[c("val_ctr", "sess_ctr", "ts_ctr")] <- 
  scale(bx_dfs[c("valence_n", "session_n", "task_switch")])
```


Put treatment cond in behavioral df

```{r}
ID_and_tx_cond <- extra_df_full %>% 
  filter(ID %in% as.numeric(unlist(bx_dfs %>% select(subj_idx) %>% 
                                     unique()))) %>% select(ID, Treatment) %>% arrange(ID)

bx_dfs$treatment_cond <- NA
if (all(ID_and_tx_cond$ID == unique(bx_dfs$subj_idx))) {
  bx_dfs <- 
    lapply(split(bx_dfs, bx_dfs$subj_idx), function(x) {
  x$treatment_cond <- 
    as.character(unlist(ID_and_tx_cond %>% filter(ID==unique(x$subj_idx)) %>% select(Treatment)))
x  
} ) %>% bind_rows()
}

bx_dfs$treatment_cond <- as.factor(bx_dfs$treatment_cond)

# Spot checks
# unique(bx_dfs[bx_dfs$subj_idx=="49", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="49", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="11", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="11", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="72", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="72", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="91", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="91", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="6", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="6", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="21", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="21", "Treatment"]
# 
# unique(bx_dfs[bx_dfs$subj_idx=="32", "treatment_cond"])
# ID_and_tx_cond[ID_and_tx_cond$ID=="32", "Treatment"]

# Basically even after exclusions w/ slightly more in FA 
table(ID_and_tx_cond$Treatment)
```


```{r}
non_completers <- names(which(table(bx_dfs$subj_idx, bx_dfs$session)[, 2]==0))
bx_dfs <- bx_dfs %>% filter(!subj_idx %in% non_completers)
length(unique(bx_dfs$subj_idx))
```

```{r}
c_bdf_c <- bx_dfs %>% filter(task=="case")
c_bdf_c$correct_n <- as.numeric(c_bdf_c$correct)

median(data.frame(c_bdf_c %>% group_by(subj_idx) %>% summarize(m=mean(correct_n)))$m)
```


```{r}
s_bdf <- bx_dfs %>% filter(task=="self")
```


Export data  
```{r}
# Just SRET 
# s_bdf <- bx_dfs %>% filter(task=="self")
# write.csv(s_bdf, "./../data/cleaned_files/s_bdf.csv")
```


Write out odd and even pre-data for split half reliability 
```{r}
pre_only <- s_bdf %>% filter(session=="Pre")
idxs <- 1:nrow(pre_only) 
even <- pre_only[idxs[lapply(idxs, "%%", 2)==0], ]
odd <- pre_only[idxs[!lapply(idxs, "%%", 2)==0], ]
table(odd$session)
table(even$session)
# write.csv(even, "../data/cleaned_files/s_bdf_even.csv")
# write.csv(odd, "../data/cleaned_files/s_bdf_odd.csv")
```
